The Astropy Project

### 2017-11-22 main.tex
fix broken \url{} to package-template

\astropy provides a package template --- as a separate \github repository,
\package{astropy/package-template}\footnote{\url{https://github.com/astropy/package-t
emplate/}} --- that aims to simplify setting up packaging, testing, and
documentation builds for developers of affiliated packages or
\astropypkg-dependent packages.
Any \python package can make use of this ready-to-go package layout, setup,
installation, and \package{Sphinx} documentation build infrastructure that was
originally developed for the \astropypkg core package and affiliated packages
maintained by the \astropy project.
The package template also provides a testing framework, template configurations
for continuous integration services, and \package{Cython} build support.

>>>>

\astropy provides a package template --- as a separate \github repository,
\package{astropy/package-template}\footnote{\url{https://github.com/astropy/package-template/}}
--- that aims to simplify setting up packaging, testing, and
documentation builds for developers of affiliated packages or
\astropypkg-dependent packages.
Any \python package can make use of this ready-to-go package layout, setup,
installation, and \package{Sphinx} documentation build infrastructure that was
originally developed for the \astropypkg core package and affiliated packages
maintained by the \astropy project.
The package template also provides a testing framework, template configurations
for continuous integration services, and \package{Cython} build support.
